{fairmetrics}: An R package for group fairness evaluation

### 2025-06-05 utils/joss_paper/paper.Rmd
fix

# Make predictions on the test set
test_data$pred <- predict(rf_model, newdata = test_data, type = "prob")

@@

#>                  Metric                          Full Metric Name GroupFemale GroupMale Difference    95% Diff CI Ratio 95% Ratio CI
#> 1                   PPR                        Statistical Parity        1.12      1.06       0.06    [0.02, 0.1]  1.06 [1.02, 1.09]
#> 2                   PPR Conditional Statistical Parity (age >=60)        1.23      1.16       0.07      [0, 0.14]  1.06    [1, 1.13]
#> 3                   FNR                         Equal Opportunity       -0.35     -0.23      -0.12  [-0.26, 0.02]  1.52  [0.9, 2.58]
#> 4                   FPR                       Predictive Equality        1.07      1.03       0.04   [0.01, 0.07]  1.04 [1.01, 1.07]
#> 5  Avg. Predicted Prob.                Balance for Positive Class        0.50      0.50       0.00         [0, 0]  1.00       [1, 1]
#> 6  Avg. Predicted Prob.                Balance for Negative Class        0.50      0.50       0.00         [0, 0]  1.00       [1, 1]
#> 7                   PPV                Positive Predictive Parity        0.21      0.16       0.05       [0, 0.1]  1.31 [0.99, 1.74]
#> 8                   NPV                Negative Predictive Parity        0.87      0.88      -0.01  [-0.06, 0.04]  0.99 [0.74, 1.32]
#> 9           Brier Score                        Brier Score Parity        0.37      0.40      -0.03 [-0.04, -0.02]  0.92 [0.89, 0.96]
#> 10             Accuracy                   Overall Accuracy Parity        1.00      1.01      -0.01  [-0.05, 0.03]  0.99 [0.95, 1.03]
#> 11          FN/FP Ratio                        Treatment Equality        0.13      0.12       0.01  [-0.04, 0.06]  1.08  [0.73, 1.6]
```

>>>>

# Make predictions on the test set
test_data$pred <- predict(rf_model, newdata = test_data, type = "prob")[,2]

@@

#>                  Metric                          Full Metric Name GroupFemale
#> 1                   PPR                        Statistical Parity        0.17
#> 2                   PPR Conditional Statistical Parity (age >=60)        0.34
#> 3                   FNR                         Equal Opportunity        0.36
#> 4                   FPR                       Predictive Equality        0.07
#> 5  Avg. Predicted Prob.                Balance for Positive Class        0.46
#> 6  Avg. Predicted Prob.                Balance for Negative Class        0.15
#> 7                   PPV                Positive Predictive Parity        0.64
#> 8                   NPV                Negative Predictive Parity        0.93
#> 9           Brier Score                        Brier Score Parity        0.09
#> 10             Accuracy                   Overall Accuracy Parity        0.88
#> 11          FN/FP Ratio                        Treatment Equality        1.00
#>    GroupMale Difference    95% Diff CI Ratio 95% Ratio CI
#> 1       0.09       0.08   [0.04, 0.12]  1.89 [1.34, 2.67]
#> 2       0.24       0.10   [0.02, 0.18]  1.42 [1.05, 1.91]
#> 3       0.58      -0.22 [-0.37, -0.07]  0.62 [0.43, 0.89]
#> 4       0.03       0.04   [0.01, 0.07]  2.33 [1.19, 4.56]
#> 5       0.37       0.09   [0.04, 0.14]  1.24 [1.09, 1.42]
#> 6       0.10       0.05   [0.03, 0.07]  1.50 [1.29, 1.75]
#> 7       0.69      -0.05  [-0.21, 0.11]  0.93 [0.72, 1.19]
#> 8       0.91       0.02  [-0.15, 0.19]  1.02 [0.79, 1.32]
#> 9       0.08       0.01  [-0.01, 0.03]  1.12 [0.88, 1.43]
#> 10      0.89      -0.01  [-0.05, 0.03]  0.99 [0.95, 1.03]
#> 11      3.00      -2.00  [-4.11, 0.11]  0.33 [0.15, 0.73]

```
